Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-12-03 papers/thesis-kirstie/thesis.tex
spelling

\section{Soft Fundamental Measure Theory (SFMT)}
Soft Fundamental Measure Theory (SFMT) is a method for forming an 
expression for the excess Helmholtz free energy of a soft-sphere fluid.
In the next chapter, 
we will adapt an SFMT functional to fit the soft-sphere WCA fluid.
Recall that in order to apply classical Density Functional Theory 
to a system that has a fixed temperature, volume, and number of particles, 
a functional for the Helmholtz free energy must first be formed. 
The ideal portion of the Helmholtz free energy is given by 
Equation~\ref{eq:Fideal-n(r)}, but forming an expression for the excess 
Helmholtz free energy from Equation~\ref{eq:Fexcess-simplified} for the 
particular fluid being modeled can be challenging. 
SFMT is a method for forming an 
expression for the excess Helmholtz free energy
that does not depend on explicitly taking into account the interaction 
that each sphere with every other sphere in the fluid (as required by 
Equation~\ref{eq:Fexcess-simplified}).
%In the next chapter on methods, we will use an SFMT functional that we 
%adapt to fit the soft-sphere WCA fluid.
SFMT was developed by Schmidt~\cite{schmidt1999density, schmidt2000fluid} 
for soft-spheres, and is an extension of Fundamental Measure Theory (FMT) 
originally developed by 
Rosenfeld~\cite{rosenfeld1989, rosenfeld1994, rosenfeld1996, fmtfromsptandsignerror} 
for the hard-sphere fluid. FMT in turn extented  
Scaled Particle Theory (SPT)~\cite{ReissSPT, santos2012phi3}, which was 
developed for homogeneous hard-sphere fluids, 
to inhomogeneous, or non-uniform hard-sphere fluids.

>>>>

\section{Soft Fundamental Measure Theory (SFMT)}
Soft Fundamental Measure Theory (SFMT) is a method for forming an 
expression for the excess Helmholtz free energy of a soft-sphere fluid.
In the next chapter, 
we will adapt an SFMT functional to fit the soft-sphere WCA fluid.
Recall that in order to apply classical Density Functional Theory 
to a system that has a fixed temperature, volume, and number of particles, 
a functional for the Helmholtz free energy must first be formed. 
The ideal portion of the Helmholtz free energy is given by 
Equation~\ref{eq:Fideal-n(r)}, but forming an expression for the excess 
Helmholtz free energy from Equation~\ref{eq:Fexcess-simplified} for the 
particular fluid being modeled can be challenging. 
SFMT is a method for forming an 
expression for the excess Helmholtz free energy
that does not depend on explicitly taking into account the interaction 
that each sphere with every other sphere in the fluid (as required by 
Equation~\ref{eq:Fexcess-simplified}).
%In the next chapter on methods, we will use an SFMT functional that we 
%adapt to fit the soft-sphere WCA fluid.
SFMT was developed by Schmidt~\cite{schmidt1999density, schmidt2000fluid} 
for soft-spheres, and is an extension of Fundamental Measure Theory (FMT) 
originally developed by 
Rosenfeld~\cite{rosenfeld1989, rosenfeld1994, rosenfeld1996, fmtfromsptandsignerror} 
for the hard-sphere fluid. FMT in turn extended  
Scaled Particle Theory (SPT)~\cite{ReissSPT, santos2012phi3}, which was 
developed for homogeneous hard-sphere fluids, 
to inhomogeneous, or non-uniform hard-sphere fluids.
